Black swans in ecological time series\\ Black swans in population dynamics\\ Heavy-tailed ecological time series\\ Black swans in ecological dynamics\\ Black swan ecological dynamics\\ \ldots

### 2014-10-20 text/ms.tex
Tweak intro paragraph

Existing evidence for black swans or heavy tails in population dynamics is
mostly anecdotal or for particular systems. For example, \citet{doak2008}
reviewed a collection of field experiment population dynamic surprises and
conclude that these are more common than we typically assume. \citet{nunez2012}
compiled a list of major events on geologic and contemporary scales that could
be considered ecological black swans. Other work has identified heavy-tail
dynamics for particular systems. For example, \citet{segura2013} identified
heavy tails in time series of marine microbe populations and \citet{drake2014}
identified heavy tails in time to extinction for experimental waterflea
populations. However, systematic evidence has remained elusive.
\citet{keitt1998} tested for power-law tail distributions in breeding bird
abundance, but later worked showed the apparent heavy tails were a result of
mixing populations of different species \citep{allen2001}. A large scale
analysis of the Global Population Dynamics Database (GPDD) by
\citet{halley2002} found little evidence for heavy-tail distributions in longer
abundance time series.

>>>>

%Existing evidence for black swans or heavy tails in population dynamics is
%mostly anecdotal or for particular systems.
There is compelling anecdotal evidence for ecological black swans, and
quantitative evidence for a limited number of systems, but systematic evidence
has been elusive. For example, \citet{doak2008} reviewed a collection of field
experiment population dynamic surprises and conclude that these are more common
than we typically assume. \citet{nunez2012} compiled a list of major events on
geologic and contemporary scales that could be considered ecological black
swans. Other work has identified heavy-tail dynamics for particular systems.
For example, \citet{segura2013} identified heavy tails in time series of marine
microbe populations and \citet{drake2014} identified heavy tails in time to
extinction for experimental waterflea populations. However, systematic evidence
has been limited. \citet{keitt1998} tested for power-law tail distributions in
breeding bird abundance, but later worked showed the apparent heavy tails were
a result of mixing populations of different species \citep{allen2001}. A later
large scale analysis of the Global Population Dynamics Database (GPDD) by
\citet{halley2002} found little evidence for heavy-tail distributions in longer
abundance time series.
